Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-05-07 Manuscript/manuscriptPSsuppl.tex
Update manuscriptPSsuppl.tex

Simulations of POPC:POPS (5:1) ans POPC:POPS (1:1) mixtures containing total 300 lipids
with potassium countertions were ran using CHARMM36 force field.
The data are available from Refs. \citenum{POPC5POPS1noCaClCHARMM} and  \citenum{POPC1POPS1noCaClCHARMM}
\todo{J. Madsen, please write simulation details}. \\

@@

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium} \\
POPC:POPS (5:1) mixtures containing total 300 (250:50) lipids
were simulated with the additional calcium concentrations.
The data is available from Refs. \citenum{POPC5POPS1withCaClCHARMM} and \citenum{POPC5POPS1with1MCaClCHARMM}.
\todo{J. Madsen, please write simulation details}. \\

>>>>

Simulations of POPC:POPS (5:1) ans POPC:POPS (1:1) mixtures containing total 300 lipids
with potassium countertions were ran using CHARMM36 force field.
The data are available from Refs. \citenum{POPC5POPS1noCaClCHARMM} and \citenum{POPC1POPS1noCaClCHARMM}
POPC:POPS (both 1:1 and 5:1) mixtures were prepared with 300 lipids in total (150:150 and 250:50, respectively) with the neutralizing ions with the CHARMM-GUI \cite{lee16,jo18}. Systems were simulated using Gromacs 5 \cite{abraham2015gromacs} and CHARMM36 force field with the simulation parameters given by the CHARMM-GUI at 298 K. For further details see table \ref{mixedIONsystemsMONOVALENT}. 
 \\

@@

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium} \\
POPC:POPS (5:1) mixtures containing total 300 (250:50) lipids
were simulated with the additional calcium concentrations.
The data is available from Refs. \citenum{POPC5POPS1withCaClCHARMM} and \citenum{POPC5POPS1with1MCaClCHARMM}.
Systems with 0.15 M and 1 M calcium chloride were prepared using the CHARMM-GUI \cite{lee16,jo18}. Systems were simulated using Gromacs 5 \cite{abraham2015gromacs} and CHARMM36 force field with the simulation parameters given by the CHARMM-GUI at 298 K. For further details see table S1. \\
